---
title: "Conditional probabilities coding practice"
author: "Your name"
date: "2024-10-03"
output: html_document
---

Today’s data comes from a study of conducted in Whickham, England. In this study, the researchers recorded each participant’s age, smoking status at the start of the study, and their health outcome 20 years later.

The data is in the mosaicData package. *You will have to install the package first!* Then run the following code:

```{r message=FALSE}
library(tidyverse)
library(mosaicData)
```

We will work with the `Whickham` data. You should open its Help file and take a view of the data before proceeding. Note that "factor" can be though of as a categorical variable. **Make sure you understand the data before proceeding!**

*Discuss with your group: What would you expect the relationship between smoking status and health outcome to be?*

1.  Create an appropriate visualization depicting the relationship between smoking status and health outcome.

```{r}

```

2.  Using wrangling code, calculate the conditional probabilities of death of each smoking status. Please report only the probabilities for when `outcome` is Dead.

```{r}

```

*With your group, briefly describe the relationship and whether or not it is what you expected. You may want to discuss the visualization from the previous exercise as well.*

3.  Create a new variable for future use called `age_cat` that takes the values as follows:

-   "18-44": if someone is less than or equal to 44 years old
-   "45-64": if someone is between 45 and 64 years old, inclusive
-   "65+": if someone is older than 64

```{r}

```

4.  Re-create your first visualization, this time faceting by `age_cat`. You are welcome to copy-paste code if that is helpful.

```{r}

```

5.  Extend your table from above by breaking it down by age category. You are welcome to copy-paste code if that is helpful.

```{r}

```

*With your group, compare the two visualizations and the two summary tables. What changed, and what might explain the change?*
