---
title: 'STAT 201: Problem Set 6 (R)'
author: "Your name"
date: 'Due: 10/28/24 at 11:59pm'
output:
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r packages, message = F}
library(tidyverse)
library(openintro)
knitr::opts_chunk$set(fig.width=6, fig.height=3) 
```

We will use the `possum` data from the `openintro` library. Take a look at the Help file and the data before proceeding. **For this homework, assume the observations were collected via a random sample.**

**Also, your code will continue to be graded for reproducibility and "clean code". If you make figures, make sure to have informative axis labels.**

## Part 1

We will obtain a 95% confidence interval for the average total length of possums from Victoria.

1.  Are the conditions for inference satisfied? Explain. You may (and should!) write code in the following R chunk to help you answer this question.

```{r}

```

**Answer:**

2.  Regardless of how you answered in (1), obtain a 95% confidence interval for the average total length of possums from Victoria. Interpret your confidence interval in context.

Be as reproducible as possible, and report your answer using in-line code.

```{r}
# start by creating vector(s) representing the data of interest for this problem

# now obtain necessary quantities 

```

**Answer:**

## Part 2

Is the average tail length of possums 5 years old or younger in Victoria different from the average tail length of possums 5 years old or younger in New South Wales or Queensland? We will obtain a confidence interval to answer this question.

3.  Are the conditions for inference satisfied? Explain. You may (and should!) write code in the following R chunk to help you answer this question. (*Hint: does making a faceted plot sound interesting to you?*)

```{r}

```

**Answer:**

4.  Regardless of how you answered in (1), obtain a 90% confidence interval appropriate for the research question. Be as reproducible as possible, and report your answer using in-line code.

```{r}
# start by creating vector(s) representing the data of interest for this problem

# now obtain necessary quantities 

```

**Answer:**

5.  Interpret the confidence interval in context and answer the research question using your interval as support.

**Answer:**
