---
title: "HT for single proportion"
author: "Practice problems"
date: "October 28, 2024"
format:
  pdf:
    keep-tex: true
    include-in-header:
      text: |
        \setkomafont{author}{\small}
        \setkomafont{date}{\small}
    geometry:
      - left=1in
      - right=1in
      - top=1in
---

```{r echo = F, message = F, warning = F}
library(tidyverse)
library(openintro)
library(knitr)
opts_chunk$set(fig.width=12, fig.height=4) 
```

1.  A recent poll found that 11% of US adults say they have smoked cigarettes in the past week, a historical low. In a random sample of 730 randomly selected students at four-year colleges, it was found that 66 students have smoked cigarettes in the past week. Test that claim that the smoking rate of students at four-year colleges is the same the national US adult average at the 0.05 significance level.

2.  An apple farmer has historically lost an average of 4% of his trees each year. He believes that he has been losing more trees lately.

    a.  In a sample of 300 trees, 20 have died. Test the farmer's claim at the 0.01 level.

    b.  How would the situation change if the farmer's sample size had been 200 instead of 300?

```{r echo = F}
n <- 850
x <- 136
p_hat <- x/n
ci <- round(p_hat + qnorm(0.975)*sqrt(p_hat *(1-p_hat)/n) * c(-1,1), 3)

p0 <- 0.182
p_val <- pnorm((p_hat - p0)/sqrt(p0 * (1-p0)/n))

```

3.  $(^*)$ A survey was conducted on 850 randomly sampled student loan borrowers, asking them if they owed more than \$30,000 in student debt. A 95% confidence interval for the true proportion of student loan borrowers with at \$30,000 of debt was found to be (`r ci`).
    a.  Based on this information, out of the 850 respondents, how many answered "yes" to the question? Justify your answer.
    b.  Use hypothesis testing to examine the claim that fewer than 18.2% of all student loan borrowers owe at least \$30,000 at the 0.05 significance level.
