---
title: "More data wrangling"
author: "Becky Tang"
date: "2024-08-15"
output: html_document
---

```{r setup, message = F}
# load libraries here
library(tidyverse)

## modify this line accordingly!
datascience <- read_csv("data/datascience_survey.csv")
```

## Warm-up exercises

How many different programming languages were recommended in the survey?

```{r}

```

How many of the respondents who work in academia in the United States are at most 25 years old at the time taking the survey?

```{r}

```

## Group analysis

I want your to generate your own investigation. Using your data-wrangling skills, try to find some interesting conclusions. After about a half hour, your group will share your process and results with the rest of the class!

Your final results must include:

-   Summary statistics or frequency table

-   Visualization

-   Comments of your code using the pound-symbol (`#`) to describe what you are doing in each code chunk

You can create more than one visualization and/or more than one table. Whatever speaks to you! The individual components (i.e. table/summary stats vs plot) do not need to use the same set of variables. Feel free to create as many code chunks as you'd like! There is a data dictionary below that defines all the variables in the data set for you.

As a stretch goal, I encourage you to try using `mutate()` and/or `group_by()` somewhere in your analysis, but it isn't necessary!

## Data dictionary

Below is the data dictionary for the subset of the Kaggle data data.

| variable               | class     | description                                                                                                           |
|:----------------------------------|:-----------------|:------------------|
| Country                | character | Home country of employee                                                                                              |
| Gender                 | character | Selected gender, one of "A different identity", "Female", "Male", "Non-binary, genderqueer, or gender non-conforming" |
| Age                    | double    | Age at time of survey                                                                                                 |
| EmploymentStatus       | character | One of "Employed full-time", "Employed part-time", or "Independent contractor, freelancer, or self-employed           |
| EmployerIndustry       | character | Industry of current employer                                                                                          |
| FormalEducation        | character | Highest level of education                                                                                            |
| Major                  | character | College major                                                                                                         |
| CompensationAmount     | double    | Total compensation                                                                                                    |
| CompensationCurrency   | character | 3-letter currency code for day-to-day currency                                                                        |
| CurrentJobTitle        | character | Job title                                                                                                             |
| TitleFit               | character | Assessment of how well title fits actual duties. One of "Fine", "Perfectly", "Poorly"                                 |
| LanguageRecommendation | character | Recommended programming language                                                                                      |
| WorkDataVisualizations | character | Proportion of job dedicated to creating data visualizations, broken into pre-determined categories                    |
| JobSatisfaction        | character | Rating of job satisfaction on scale of 1-10, where 1 is not satisfied and 10 is highly satisfied                      |
| JobSatisfaction2       | double    | Rating of job satisfaction on scale of 1-10, where 1 is not satisfied and 10 is highly satisfied                      |
| ConversionUSD          | double    | Conversion factor from `CompensationCurrency` to USD.                                                                 |
