---
title: "Null distribution of sample proportion"
date: "October 14, 2024"
---

```{r message = F}
library(tidyverse)
```

Define $p$ as the true proportion of students who get at least 7 hours of sleep on average. Our hypotheses were:

$H_{0}$: $p \leq 0.5$

$H_{A}$: $p > 0.5$

## Simulating null distribution

The example below demonstrates how to obtain a null distribution for $\hat{p}$ under $H_{0}$. We said:

-   pink slips represent students who get at least 7 hours, and

-   purple slips represent students who do not get at least 7 hours

```{r}
set.seed(2)
B <- 5000
n <- 10
p_null_vec <- rep(NA, B)
for(b in 1:B){
  null_samp <- sample(x = c("pink", "purple"),
                      size = n, 
                      replace = T, 
                      prob = c(0.5, 0.5)) 
  
  p_null_vec[b] <- sum(null_samp == "pink")/n
}
```

The code above repeatedly for `r B` iterations draws a new sample of size `r n` from the world assuming $H_{0}$ is true (in this case, $p = 0.5$). At every iteration, we record the proportion of pink slips in the sample of size `r n` to represent the proportion of people who got at least 7 hours of sleep.

## Visualizing null distribution

We can visualize the null distribution by:

1.  Creating a data frame of our vector of simulated null statistics `p_null_vec`
2.  Piping into `ggplot()`

::: column-margin
`data.frame(<variable name> = <vector>)`creates a data frame from vectors, and we can set the column/variable names.

In the code here, `data.frame(p_sim = p_null_vec)` creates a data frame with a variable called `p_sim`. The values that comprise that variable come from `p_null_vec`.
:::

```{r fig.height=4}
null_df <- data.frame(p_sim = p_null_vec)
ggplot(null_df, aes(x = p_sim))+
  geom_histogram(binwidth = 0.1,col = "white")+
  labs(x = "Null dist. of proportion of students getting at least 7 hours") +
  theme_minimal()
```

We can add a vertical line to our plot to show where the observed $\hat{p}$ falls in the null distribution.
