---
title: "Knitting beautiful tables"
---

```{r message = F, warning = F, echo = F}
library(tidyverse)
library(openintro)
library(broom)
```

You may have noticed that the data frames are not the most beautiful in the knitted output. With the help of the `knitr` package, we can make the tables knit beautifully. **When you knit for the first time, it may take a minute or two as more things get installed. Don't panic! It will knit!**

1.  At the top of your document, load in the `knitr` package: `library(knitr)`.
    -   You may need to install this package first. Either do this in the "Packages" tab on the right, or in the **Console** by typing `install.packages("knitr")`.
2.  Then for any data frame/table you'd like to knit beautifully, just pipe directly to the `kable()` function. For example:

```{r}
library(knitr)
mod <- lm(volume ~ diam, data = cherry)
## equivalently: kable(tidy(mod))
tidy(mod) |>
  kable()
```

Compare this to when we don't use `kable()`:

```{r}
tidy(mod)
```

You can control the number of digits shown in the table:

```{r}
tidy(mod) |>
  kable(digits = 3)
```

Look at the Help file for more customization!
