---
title: "Introduction to MLR"
subtitle: "Categorical predictor (more than two levels)"
---

```{r message = F}
library(tidyverse)
library(broom)
```

## Birth weight data

Baystate Medical Center, Springfield, MA during 1986 on the birth weights of 189 babies, along with descriptive information about the mother

```{r}
library(readr)
birthwt <- read.csv("https://raw.githubusercontent.com/midd-stat201-fall2024/midd-stat201-fall2024.github.io/refs/heads/main/data/birthwt.csv")
```

We want to understand risk factors for a baby's birth weight (`bwt`). Homework 8 explores the effect of mother's `smoke` status on birth weight of baby.

Let's look at a different variable: `race` of mother

  -  Variable `race` is numerical where 1 = white, 2 = black, 3 = other

```{r}
# wrong! This is bad!!
lm(bwt ~ race, data = birthwt) |>
  tidy()
```

## Converting to factor

We need to convert `race` variable to categorical! 

```{r echo = T}
birthwt2 <- birthwt |>
  mutate(race = case_when(race == 1 ~ "white",
                          race == 2 ~ "black",
                          race == 3 ~ "other")) |>
  mutate(race = factor(race, levels = c("white", "black", "other")))

str(birthwt2$race)
```

Let's go ahead and fit this model using `lm()` as we usually would and look at the tidy output:

```{r}
bwt_lm <- lm(bwt ~ race, data = birthwt2)
tidy(bwt_lm)
```

Let's write out the form of the linear regression model:
