---
title: "Randomization for difference in proportions"
date: "October 16, 2024"
---

```{r message = F}
library(tidyverse)
library(openintro)
```

We are using the `cpr` data from the `openintro` library. Define $p_{T}$ as the proportion of treatment group who survived, $p_{C}$ as the proportion of control group who survived. Our hypotheses were:

$H_{0}$: $p_{T} - p_{C} \leq 0$ versus $H_{A}$: $p_{T} - p_{C} > 0$

## Simulating null distribution

We will store some values as objects in R for reproducibility.

```{r}
# get the observed outcomes as a vector
outcomes <- cpr$outcome

# store number of treatment and control observations from original sample
n_t <- sum(cpr$group == "treatment")
n_t
n_c <- sum(cpr$group == "control")
n_c

# get observed difference in proportions

# option 1
obs_diff <- cpr |>
  group_by(group) |>
  summarise(p = mean(outcome == "survived")) |>
  pull(p) |>
  diff() # defaults to taking second value minus first

# option 2
cond_probs <- cpr |>
  group_by(group) |>
  summarise(p = mean(outcome == "survived")) |>
  pull(p)
obs_dff <- cond_probs[2] - cond_probs[1]
obs_diff
```

Now we will perform the randomization test!

::: column-margin
If you only pass in a vector as the argument to `sample()` without specifying the size of the sample, you will get a shuffled version of the vector back as output. That is, the function will resample without replacement from the vector, with the size being the same size as the vector.
:::

```{r}
set.seed(310)
B <- 1000
diff_sims <- rep(NA , B)
for(b in 1:B){
  # shuffle the outcomes. See comment for more details.
  shuffled <- sample(outcomes)
  
  # deal out first n_t cards to treatment group
  treat_sim <- shuffled[1:n_t]
  
  # deal out remaining n_c cards to control group
  control_sim <- shuffled[-c(1:n_t)]
  
  # calculate proportion of survival in each group
  p_t_sim <- sum(treat_sim == "survived")/n_t
  p_c_sim <- sum(control_sim == "survived")/n_c
  
  # calculate difference and store. 
  # I will do treatment - control because it mirrors how obs_diff is calculated
  diff_sims[b] <- p_t_sim - p_c_sim
}
```

## Visualize null distribution

```{r echo = F, fig.height=3, echo = F}
data.frame(diffs = diff_sims) |>
  ggplot(aes(x = diffs)) +
  geom_histogram(binwidth = 0.025, center = 0.0125, col = "white")+
  labs(x = "Null dist. of difference in survival rates (treat - control)", caption = "Vertical line = observed difference") +
  theme(text = element_text(size= 16)) +
  geom_vline(xintercept = obs_diff, col = "magenta")
```

## Obtain p-value

We need to find how many simulated null differences in proportions were greater than or equal to our observed difference of `obs_diff` = `r obs_diff`.

```{r}
p_val <- sum(diff_sims >= obs_diff) / B
p_val
```
