---
title: "Intro to R coding practice"
author: "Your name here"
date: "Due: 9/12/2024 at 11:59pm"
output: html_document
---

1.  Change your name in the YAML. Be sure to keep the quotation marks!

2.  Execute the following the code in the code chunk. Describe in words what the code is doing.

```{r}
1:10
```

**Answer**:

3.  We will learn how to use the important function `sample()`, which allows us to obtain a random sample. Look at the help file by typing `?sample` into your Console. After some experimenting, write code randomly sample two numbers from the set of numbers 1-5, without replacement. Note: it's okay if you get something different from those around you! We are *random*ly sampling after all!

```{r}

```

4.  In the following code chunk, write code to load in the `openintro` package. Then run the code in the code chunk.

```{r}

```

5.  In the Console, type in `?cherry` to open up the Help file for the `cherry` data frame. Type into the white space below the units for each of the variables.

**Answer**:

6.  Remember that rows in data frames represents observations. How many observations are there in the `cherry` data frame? Answer this by using the `nrow()` function and passing in the name of data frame of interest. You can confirm your answer by looking at the `cherry` Help file.

```{r}

```

Once you're finished, be sure to knit and submit the outputted file to the corresponding Canvas assignment!
