---
title: "Bootstrap confidence intervals"
author: "Your name"
date: "Due: 10/14/24 at 11:59pm"
output: html_document
---

We will work with the average hours of sleep each class reported. In the following code chunk, please delete the line of code that does not correspond to your section.

```{r message=FALSE}
library(tidyverse)
library(readr)

# SECTION A DATA
url_file <- "https://raw.githubusercontent.com/midd-stat201-fall2024/midd-stat201-fall2024.github.io/refs/heads/main/data/sectionA_week4_sleep.csv"

# SECTION B DATA 
url_file <- "https://raw.githubusercontent.com/midd-stat201-fall2024/midd-stat201-fall2024.github.io/refs/heads/main/data/sectionB_week4_sleep.csv"


sleep <- read_csv(url_file)
```

We will intialize a pseudo-random-number-generator using the `set.seed()` function. You can choose any whole number to input as the parameter to this function. If I have the same seed and code and you, then I can reproduce the same random results.

```{r}
set.seed(201)
```

1.  Create a variable that represents and stores the target sample size: 10. Then, take a random sample of size 10 of sleep hours from our population. Store your sample into a variable called `x`.

```{r}
# create a variable for sample size

# obtain and store our sample

```

2.  We will take 5000 bootstrap iterations. Store this value as a variable for reproducibility.

```{r}
# store number of bootstrap iterations
```

3.  Obtain a bootstrap distribution of sample means using your original sample. *Remember to store the bootstrap statistics somewhere! Please use a meaningful variable name.* It may be useful to look at and modify the live code from previous class (on website)

```{r}

```

4.  The `quantile()` function obtains percentiles for us. It requires two arguments: a numeric vector and a percentile level (between 0 and 1). For example, `quantile(x, 0.5)` finds the 50-th percentile of the vector `x`.

Using this function, obtain the bounds for a 80%, 90%, and 99% bootstrap confidence interval, respectively. Store these bounds as variables.

```{r}
# 80%

# 90%

# 99%
```

5. Report the three confidence intervals here in the format of (lower, upper) *using in-line code*. 

80% CI:

90%: CI:

99% CI: 

6.  How do the confidence interval widths change as the level of confidence increases?

**Answer:**

7.  Interpret one of your confidence intervals in context. *Use in-line code in your answer.*

**Answer:**
