---
title: "Pivoting + HT coding practice"
author: "Your name"
date: "Due: 11/4/2024 at 11:59pm"
output: html_document
---

```{r setup, message =FALSE}
library(tidyverse)
diamond_price <- read_csv("https://raw.githubusercontent.com/midd-stat201-fall2024/midd-stat201-fall2024.github.io/refs/heads/main/data/diamonds.csv")
```

1.  Wrangle/manipulate the `diamond_price` data frame into the long format. Ensure that the variable names you end up choosing are informative/meaningful. Store the resulting data frame into a new data frame called `diamond_price_long`.

```{r}

```

2.  Using your new data frame, check if the conditions for the CLT-based hypothesis test are satisfied.

```{r}

```

**Answer:**

3.  (Optional) Obtain your test statistic and p-value. Report your p-value using in-line code.

```{r}

```

**Answer:**

4.  (Optional) Conduct your simulation-based hypothesis test for the same set of hypotheses. Report your p-value using in-line code.

```{r}

```

**Answer:**

Once finished, knit once more and submit the HTML to Canvas!
