---
title: "Data wrangling coding practice"
author: "Your name"
date: "Due: 09/25/24 at 11:59pm"
output: html_document
---

1.  Load in the `tidyverse` and `openintro` packages the in the code chunk below. We will once again work with the `starbucks` data from the `openintro` package. Remember that if you want to look at the data, you can type `View(data frame name)` in the *Console*.

```{r}
# load packages here

```

2.  Wrangle the data to display the five items with the highest amount of calories. Only display the name of the items and their calorie content.

```{r}

```

3.  Wrangle the data to display all the sandwich items in the data set.

```{r}

```

4.  Three macronutrients serve as sources of calories (i.e. energy) in food: carbohydrates, proteins, and fat. Carbohydrates contain 4 calories per gram, proteins contain 4 calories per gram, and fats contain 9 calories per gram.

Wrangle the data to add a new variable called `theoretical_cals` which represents the number of calories each item in the `starbucks` data theoretically should have based on its levels of carbohydrates, protein, and fat. Store the resulting data frame as a new data frame called `starbucks_new`.

```{r}

```

5.  Using your `starbucks_new` data frame from the previous step, display a summary table/data frame that shows the standard deviation of the differences between the reported calories and theoretical calories. Make sure to specify an informative/nicer name in your summary table.

```{r}

```

Once you're finished, be sure to knit and submit the outputted HTML file to the corresponding Canvas assignment!
