---
title: "Data wrangling coding practice"
author: "Your name"
date: "Due: 09/25/24 at 11:59pm"
output: html_document
---

1.  Load in the `tidyverse` and `openintro` packages the in the code chunk below. We will once again work with the `starbucks` data from the `openintro` package. Remember that if you want to look at the data, you can type `View(<data frame name>)` in the *Console*.

```{r}
# load packages here

```

2.  Wrangle the data to display the five items with the highest amount of calories. Only display the name of the items and the calorie content.

```{r}

```

3.  One gram of protein contains 4 calories. Wrangle the data to add a new variable called `prop_protein` which represents the proportion of the item's calories that are due to protein. Store the resulting data frame as a new variable called `starbucks_new`.

```{r}


```

4.  Using your `starbucks_new` data frame from the previous step, display a summary table/data frame that shows the median proportion of calories that come from protein for each `type` of Starbucks item in *ascending* order.

```{r}

```

Once you're finished, be sure to knit and submit the output file to the corresponding Canvas assignment!
