---
title: "Numerical data coding practice"
author: "Your name"
date: "Due: 9/16/2024 at 11:59pm"
output: html_document
---

```{r packages, message = F}

```

1.  Change your name in the YAML. Be sure to keep the quotation marks!

2.  In the following code chunk, load in `openintro` package. Then run the code in the code chunk. We will once again work with the `cherry` data set.

```{r}

```

3.  Remember that columns of a data frame represent variables. We can access a specific variable by typing the name of the data frame, followed by a dollar sign, and the name of the variable of interest (e.g. `dataframe$variable_name`). In the code chunk below, access the diameter variable from the `cherry` data frame. Execute your code.

```{r}

```

4.  Make a histogram of the diameter of cherry trees. Can you add a title to your plot?

```{r}

```

5.  Make a scatterplot of the diameter and volume of cherry trees. Put volume on the y-axis. Can you change the labels of the axes to be something nicer?

```{r}

```

Once you're finished, be sure to knit and submit the output file to the corresponding Canvas assignment!
